How cryptic is cryptic diversity? Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-05-10 documents/turtle_presentation.Rnw
lots of presentation work. need to write train randomizer.

<<message = FALSE, echo = FALSE, warning = FALSE>>=
require(knitr)
require(xtable)
require(ggplot2)
require(reshape2)
require(GGally)

opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE,
               highlight = TRUE, background = 'white',
               fig.height = 3, fig.width = 4
               , eval = FALSE
               )

source('../src/plotting_functions.r')
#load('../src/turtle_analysis.r')
@

@@

\section{Introduction}
\begin{frame}
  \frametitle{Cryptic diversity}
  % image of example taxa that are morphologically identical and are only differentiated via genetic means
\end{frame}

@@

\section{Results}
\begin{frame}
  \frametitle{Results: mophometrics}
<<gm, eval = FALSE>>=
morph <- ggpairs(turtle.adult, columns = c(1:3),
                 upper = 'blank')
fits <- procGPA(turtle.land.adult)
land <- mshape.plot(fits, all.points = TRUE)
morph <- putPlot(morph, land, 1, 3)
morph
@
\end{frame}

\begin{frame}
  \frametitle{Results: gap clustering}
<<gap, eval = FALSE>>=
gap <- gap.plot(tadult.gap)
gap
@
\end{frame}

@@

% model selection is unnecessary because of time constraints
\begin{frame}
  \frametitle{Results: multinomial logistic regression}

@@

\begin{frame}
  \frametitle{Results: random forests}
  % plot the ROC curves
  % four facets, multiple lines
\end{frame}

\section{Discussion}
\begin{frame}
  \frametitle{Best classification scheme}
\end{frame}

\begin{frame}
  \frametitle{Future}
\end{frame}

>>>>

<<message = FALSE, echo = FALSE, warning = FALSE>>=
require(knitr)
require(xtable)
require(grid)
require(ggplot2)
require(reshape2)
require(GGally)
require(scales)

opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE,
               highlight = TRUE, background = 'white',
               fig.height = 3, fig.width = 4
               , eval = TRUE
               )

theme_set(theme_bw())

source('../src/plotting_functions.r')
load('../data/turtle_analysis.RData')
@

@@

\section{Introduction}
\begin{frame}
  \frametitle{Cryptic diversity}
  % image of example taxa that are morphologically identical and are only differentiated via genetic means
  %
  How much of cryptic diversity is just a function of sample size?
\end{frame}

@@

\section{Results}
\begin{frame}[fragile]
  \frametitle{Results: mophometrics}
<<gm, results = 'hide', fig.width = 3.5, fig.height = 3.5, eval = TRUE>>=
morph <- ggpairs(turtle.adult, columns = c(1:3),
                 upper = 'blank',
                 params = c(LabelSize = 2, gridLabelSize = 2, size = 1))
fits <- procGPA(turtle.land.adult)
land <- mshape.plot(fits)
morph <- putPlot(morph, land, 1, 3)
morph
@

\begin{frame}[fragile]
  \frametitle{Results: gap clustering}
<<gap, fig.width = 4, fig.height = 3,  eval = TRUE>>=
gap <- gap.plot(tadult.gap)
gap <- gap + theme(axis.title = element_text(size = 7.5),
                   axis.text = element_text(size = 6))
gap
@
\end{frame}

@@

% model selection is unnecessary because of time constraints
\begin{frame}[fragile]
  \frametitle{ROC}
<<roc, eval = TRUE>>=
rf.rocs <- lapply(trf.a, function(x) {
                  rr <- x$results$ROC
                  rr})
rf.rocs <- ldply(rf.rocs)
multi.rocs <- lapply(tm.a, function(x) {
                     lapply(x, function(y) {
                            rr <- max(y$results$ROC)
                            rr})})
multi.rocs <- ldply(lapply(lapply(multi.rocs, ldply), t))

names(rf.rocs) <- names(multi.rocs) 
roc.mod <- rbind(rf.rocs, multi.rocs)
mod.names <- c(rep('rf', nrow(rf.rocs)), rep('multi', nrow(multi.rocs)))
roc.mod <- cbind(mod.names, roc.mod)
roc.mod <- melt(roc.mod)
roc.mod$variable <- as.numeric(roc.mod$variable)

ggroc <- ggplot(roc.mod, aes(x = variable, y = value, color = mod.names))
ggroc <- ggroc + geom_line()
ggroc <- ggroc + scale_x_continuous(breaks = seq(max(roc.mod$variable)))
ggroc <- ggroc + scale_color_discrete(labels = c('multinomial', 
                                                 'random forest'))
ggroc <- ggroc + theme(legend.title = element_blank(),
                       legend.position = 'right',
                       legend.margin = unit(0, 'cm'),
                       legend.text = element_text(size = 5),
                       axis.title = element_text(size = 8),
                       axis.text = element_text(size = 5))
ggroc <- ggroc + labs(x = '# of features', y = 'AUC ROC')
ggroc <- ggroc + facet_wrap(~.id)
ggroc
@

@@

\begin{frame}
  \frametitle{Are the AUC ROC values meaningful?}
\end{frame}

\begin{frame}
  \frametitle{Best classification scheme}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Variable importance}
  % ggpairs from the best random forest model
<<imp, fig.width = 3.5, fig.height = 3.5, eval = TRUE>>=
most.imp <- trf.a$spinks$optVariables
ww <- 'spinks'
ggimp <- ggpairs(turtle.adult,
                 columns = c(most.imp[1:3], ww), 
                 colour = 'spinks',
                 upper = 'blank',
                 params = c(LabelSize = 2, gridLabelSize = 2, size = 1))
ggimp
@
\end{frame}

\section{Discussion}
\begin{frame}
  \frametitle{Future}
\end{frame}
